Clearance Project - 1 - Data Generation

### 2025-03-19 data-raw/ClearanceProject-1-DataRmd.Rmd
Merge feature/Rclearance_comparison to dev (#22)
* Added diff_log_cvt() call for oral and iv.

* Changed log_likelihood() to work with pre-calculated predictions from other sources. Still requires sigma.

* Quick fix to get_fit.pk which no longer needs unnesting.

* Renamed and initialized 4 analysis documents for clearance project.

* Added data associated with clearance project for efficient loading.

* Organized ongoing hepatic clearance project files in data-raw/

save(rpr_param_rest_l, rpr_param_nrest_l,
     rpr_param_df, rpr_httk_clearance_df,
     rpr_httk_preds, file = "data-raw/RCdata/rat_pars_rat.RData")
```

@@

save(rph_param_rest_l, rph_param_nrest_l,
     rph_param_df, rph_httk_clearance_df,
     rph_httk_preds,
     file = "data-raw/RCdata/rat_pars_human.RData")
```

>>>>

save(rpr_param_rest_l, rpr_param_nrest_l,
     rpr_param_df, rpr_httk_clearance_df,
     rpr_httk_preds, file = "data-raw/rat_pars_rat.RData")
```

@@

save(rph_param_rest_l, rph_param_nrest_l,
     rph_param_df, rph_httk_clearance_df,
     rph_httk_preds,
     file = "data-raw/rat_pars_human.RData")
```
